00-OD-preparation

### 2022-04-18 00-OD-preparation.Rmd
javier s first commit - changes to OD-prep and adding silly rmd

@@

zn <- st_read("data-raw/zn.shp")
```
Importing the spatial object which corresponds to the low-emission-zones
```{r}
#XXX
```

@@

>>>>

fsdsjhdskjds
```{r}

@@

zn <- st_read("data-raw/zn.shp")
```
Importing the spatial object which corresponds to the low-emission-zones
```{r}
zn_LEZ <- st_read("data-raw/LEZ.shp") %>% transmute(ZT1259, 
                                                                       LEZ = 1)
```

Add a column which indicates if a zn is within the center of madrid:
```{r}
zn <- zn %>% merge(zn_LEZ %>% st_drop_geometry(), by = c("ZT1259"), all.x=TRUE)
```

plot and color in madrid city:
```{r}
#plot to double check that centroids are on zones
ggplot() +
  geom_sf(data = zn, aes(fill = as.factor(LEZ)), col = NA) +
  scale_fill_manual(values = c("red", "grey"), name= "Cluster Group")
```
```{r}
#plot to double check that centroids are on zones
ggplot() +
  geom_sf(data = zn_LEZ) 
```

@@

summary(OD_v$TIEMPO_VIAJES)
